---
title: "Assignment 5 - The Final Codedown, Meta-analysis of pitch in schizophrenia"
author: "Gustav, Magnus, Morten, Nicoline, Tobias"
date: "3/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Building on the shoulders of giants: meta-analysis
Data: https://www.dropbox.com/s/0l9ur0gaabr80a8/Matrix_MetaAnalysis_Diagnosis_updated290719.xlsx?dl=0
Prisma chart: https://www.dropbox.com/s/vbjf6ff73dv9tru/PRISMA%202009%20flow%20diagram_PP.pptx?dl=0 

1. Build a forest plot of the results (forest(model))
 
2. Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?

3. Now look at the output of rma() and check tau and I2

```{r}
# Loading packages and data (Tobias)
library(pacman)
pacman::p_load(metafor, readxl, tidyverse)
df <- read_excel('Matrix_MetaAnalysis_Diagnosis_updated290719.xlsx')

# Renaming column headers in dataframe and selecting what we need in our analysis (Nicoline) 
df <- df %>% rename(
  article = ArticleID,
  study = StudyID,
  specification = Specification,
  title = Title,
  authors = Authors,
  published = Year_publication,
  citation = Article,
  diagnosis = DIAGNOSIS,
  con_mean = PITCH_F0_HC_M,
  schiz_mean = PITCH_F0_SZ_M,
  con_sd = PITCH_F0_HC_SD,
  schiz_sd = PITCH_F0_SZ_SD,
  con_sd_mean = PITCH_F0SD_HC_M,
  schiz_sd_mean = PITCH_F0SD_SZ_M,
  con_sd_sd = PITCH_F0SD_HC_SD,
  schiz_sd_sd = PITCH_F0SD_SZ_SD,
  schizophrenia = SAMPLE_SIZE_SZ,
  control = SAMPLE_SIZE_HC
) %>% select(article,
             study,
             specification,
             title,
             authors,
             published,
             citation,
             diagnosis,
             con_mean,
             schiz_mean,
             con_sd,
             schiz_sd,
             con_sd_mean,
             schiz_sd_mean,
             con_sd_sd,
             schiz_sd_sd,
             schizophrenia,
             control)

#Using the escalc function to get effect sizes for both mean and standard deviation (Magnus)
df_2 <- escalc(n1i = control,
             n2i = schizophrenia,
             m1i = con_mean,
             m2i = schiz_mean,
             sd1i = con_sd,
             sd2i = schiz_sd,
             data = df,
             measure = 'SMD',
             append = TRUE)

df_3 <- escalc(n1i = control,
             n2i = schizophrenia,
             m1i = con_sd_mean,
             m2i = schiz_sd_mean,
             sd1i = con_sd_sd,
             sd2i = schiz_sd_sd,
             data = df,
             measure = 'SMD',
             append = TRUE)

# Making lmer models (Gustav)
model_mean <- lmer(yi ~ 1 + (1|Study), PitchMean_ES, weights = 1/vi, REML=F, control = lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))

model_sd <- lmer(yi ~ 1 + (1|Study), PitchSD_ES, weights = 1/vi, REML=F, control = lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
# Agreeing on the fact that it is not a good idea to use lmer models in this case ;) 

# Making pretty rma models instead!(Morten)
ma_1 <- rma(yi, vi, data = df_2)
ma_2 <- rma(yi, vi, data = df_3)
summary(ma_1)
summary(ma_2)

# Making forest plots (Tobias)
forest(ma_1, slab = paste(df$citation))
forest(ma_2, slab = paste(df$citation))
```


2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots.
```{r}
# Loading our data from assignment 3 into R (Tobias)
pitch_data <- read_csv("use_da_data.csv") 

# We need the different measures from assignment 3 in order to get them into the metaanalysis (Nicoline)
pitch_mean <- pitch_data %>% 
  group_by(subject) %>% 
  summarize(mean_pitch = mean(mean, na.rm = T), 
            mean_sd = mean(sd, na.rm = T),
            diagnosis = mean(diagnosis))

pitch_mean_group <- pitch_mean %>% 
  group_by(diagnosis) %>% 
  summarise(mean_pitch = mean(mean_pitch, na.rm = T), 
            mean_sd = mean(mean_sd, na.rm = T))

pitch_sd <- pitch_data %>% 
  group_by(subject) %>% 
  summarize(sd_mean = sd(mean, na.rm = T), 
            sd_sd = sd(sd, na.rm = T),
            diagnosis = mean(diagnosis))

pitch_sd_group <- pitch_sd %>% 
  group_by(diagnosis) %>% 
  summarise(sd_sd_mean = sd(sd_mean, na.rm = T), 
            sd_sd_sd = sd(sd_sd, na.rm = T))

sum(pitch_data$diagnosis == 0)
# 116 diagnosis 0
sum(pitch_data$diagnosis == 1)
# 105 diagnosis 1 = schiz

#Making the dataframe for our study results (Magnus)
de <- data.frame(NA, '51', NA, NA, 'Bom, Magnus, Gade, Morten, Hansen, Grønhøi, Metzsch, Gustav, Schmidt, Nicoline.', '2020', 'Metzsch et al (2020)', NA, 162.4905, 153.9958, 35.69862, 24.01674, 17.40874, 17.07090, 21.71260, 21.11099, 105, 116)
names(de) <- c('article', 'study', 'specification', 'title', 'authors', 'published', 'citation', 'diagnosis', 'con_mean', 'schiz_mean', 'con_sd', 'schiz_sd', 'con_sd_mean', 'schiz_sd_mean', 'con_sd_sd', 'schiz_sd_sd', 'schizophrenia', 'control')

# Binding our results with the dataset from metaanalysis (Tobias)
new_df <- rbind(df, de)

# Using the escalc function on our study results + all studies within metanalysis (Morten)
new_df_2 <- escalc(n1i = control,
             n2i = schizophrenia,
             m1i = con_mean,
             m2i = schiz_mean,
             sd1i = con_sd,
             sd2i = schiz_sd,
             data = new_df,
             measure = 'SMD',
             append = TRUE)

new_df_3 <- escalc(n1i = control,
             n2i = schizophrenia,
             m1i = con_sd_mean,
             m2i = schiz_sd_mean,
             sd1i = con_sd_sd,
             sd2i = schiz_sd_sd,
             data = new_df,
             measure = 'SMD',
             append = TRUE)

# Making the rma models on our own study (Gustav) 
ma_3 <- rma(yi, vi, data = new_df_2)
ma_4 <- rma(yi, vi, data = new_df_3)
summary(ma_3)
summary(ma_4)

# Making forest plots for our own study (Nicoline) 
forest(ma_3, slab = paste(new_df_2$citation))
forest(ma_4, slab = paste(new_df_3$citation))
```


3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.
```{r}
# Assessing quality of the literature by using the functions we learned about in the lecture (Gustav)
funnel(ma_2) #funnel plot 
ranktest(ma_2) #Kendall's tau 
inf <- influence(ma_2) #Influential studies
print(inf)
plot(inf)
```
